%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.7\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Alex}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Wicks}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge DevOps Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the first row of icons
	%\icon{MapMarker}{12}{London, UK}\\
	%\icon{Phone}{12}{+44 7484 6166 43}\\
	%\icon{At}{12}{\href{mailto:alex@awicks.io}{alex@awicks.io}}\\	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{London, UK}\\
	\icon{Phone}{12}{+44 7484 6166 43}\\
	\icon{At}{12}{\href{mailto:alex@awicks.io}{alex@awicks.io}}\\	
	\icon{Globe}{12}{\href{https://awicks.io}{awicks.io}}\\	
\end{minipage}

\vspace{0.4cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{About Me}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
  IT enthusiast with a keen interest in Linux, and have been using it since a young age. In recent years I have embraced DevOps \linebreak practices and technologies such as \linebreak automation, IaC, Ansible \& Kubernetes. I am a good team player but can work autonomously as required. I enjoy learning new technologies \& methodologies.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Linux}{80}
		\baritem{Kubernetes}{40}
		\baritem{Ansible}{70}
		\baritem{Python}{40}
	\end{barchart}
\end{minipage}

\iffalse
\vspace{\baselineskip}
\cvsect{Achievements}

\begin{minipage}[t]{0.5\textwidth}
\begin{itemize}
  \item Company-first git CD pipeline to production
  \item Implement Kubernetes build environment; migrate legacy workloads
\end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{itemize}
  \item Server deployment automation. Over 20 previously manual steps in Jenkins pipeline
  \item VMware private cloud in AWS implementation
\end{itemize}
\end{minipage}
\fi

\vspace{0.5cm}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
  \entry
    {Jul. '21 - Now}
    {Platform Engineer}
    {CapGemini - HMRC Market Unit}
    {Platform monitoring in a cloud-native (AWS) environment. Large-scale Prometheus monitoring (10,000s of pods), Thanos aggregation, Alertmanager, Kubernetes \linebreak integrations. Helm, Terraform deployments. Packer for building immutable \linebreak infrastucture. Consul, consul-template for service discovery/configuration.\\ \texttt{AWS}\slashsep\texttt{Prometheus}\slashsep\texttt{Terraform}\slashsep\texttt{Helm}}
	\entry
		{Sep. '20 -- Jun. '21}
		{DevOps Engineer}
		{Flextrade Systems}
    {Cross-functional working, unifying operations \& development teams, primarily working \linebreak on automation \& build environments. In-house automation tooling (Python), \linebreak Ansible. Continuous delivery. AWS EC2, Route53. VMware Cloud on AWS. Bare-metal \linebreak Kubernetes on-premises (PXE). Jenkins Pipelines as code (groovy), GitLab CI. \linebreak Containerisation (docker). Metrics-based monitoring (Prometheus, Grafana). Infrastucture-as-code (Packer).\\ \texttt{Ansible}\slashsep\texttt{Jenkins}\slashsep\texttt{Kubernetes}\slashsep\texttt{Continuous Delivery}}
	\entry
		{2019 -- Aug. '20}
		{Systems Administrator}
		{Flextrade Systems}
    {Operations in a SaaS environment. Supporting 1,000s of Linux VMs. Citrix, VDI, \linebreak Active Directory, LDAP. Firewalls, L2 switching, iptables, tcpdump, mitmdump, \linebreak TLS troubleshooting. HAProxy \& nginx. PostgreSQL, MongoDB. Nagios. Jira, Agile methodology (sprint, kanban).\\ \texttt{Puppet}\slashsep\texttt{VMware}\slashsep\texttt{Cisco ASA, IOS}\slashsep\texttt{RHEL, CentOS}\slashsep\texttt{Ticket Triage}}
	\entry
		{Aug '17 -- 2018}
		{Junior Systems Administrator}
		{Vyper Networks}
    {First line desktop support. On-premises customer visits. Linux web \& mail server \linebreak administration.\\ \texttt{nginx}\slashsep\texttt{postfix}\slashsep\texttt{CentOS}\slashsep\texttt{Desktop Support}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{Sep. 2018}
		{Red Hat Certified System Administrator}
		{Certification ID 180-199-853}
    {}
	\entry
		{2015 -- 2017}
		{A Levels}
		{Northgate Sixth Form}
		{Mathematics, Physics, Computer Science}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - Native \\
	\textbf{Polish} - Proficient \\
	\textbf{German} - Proficient \\
  \textbf{French} - Beginner \\
  \textbf{Russian} - Beginner
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I enjoy tinkering in my home lab. I'm a massive \linebreak petrolhead and am interested in anything with a \linebreak combustion engine. I like to cycle at the weekends. I am also an avid photographer.
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
